---
title: "Planned gallery examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Planned gallery examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7, fig.height = 4.2)
```

This page tracks example figures for the pkgdown gallery. All of the surfaces
below are implemented; see package `ROADMAP.md` for design notes and known
limitations (e.g. dense-lane label overlap in swimlanes).

| Example | Primary API | Status |
|---------|-------------|--------|
| Methods / lit-review timeline | `ggtimeline()` | done |
| Clinical trial roadmap | `ggtimeline()` + `add_milestone()` / `add_span()` | done |
| Project / grant intervals | `aes(x, xend)` intervals | done |
| Multi-stream swimlanes | `ggtimeline_swimlane()` | done |
| Gantt roadmap | `ggtimeline_gantt()` | done |

## Clinical trial roadmap with milestones

```{r milestones}
library(ggplot2)
library(ggtimeline)

trials <- data.frame(
  start = as.Date(c("2021-01-01", "2022-06-01", "2023-01-01")),
  end   = as.Date(c("2021-09-01", "2023-02-01", "2023-11-01")),
  topic = c("Phase I", "Phase II", "Phase III"),
  arm   = c("A", "A", "B")
)

ggtimeline(
  trials,
  aes(x = start, xend = end, label = topic, fill = arm),
  year_breaks = "1 year"
) +
  scale_timeline_fill() +
  add_milestone(as.Date("2022-06-01"), label = "IND filing")
```

## Multi-stream swimlanes

```{r swimlanes}
data("phenotype_methods_timeline")

ggtimeline_swimlane(
  phenotype_methods_timeline,
  aes(x = date, label = topic, group = category, fill = category),
  lane_spacing = 3
) +
  scale_timeline_fill()
```

## Gantt roadmap

```{r gantt}
ggtimeline_gantt(
  trials,
  aes(x = start, xend = end, label = topic, fill = arm)
)
```
